Non-Vertical Cultural Transmission, Assortment, \\and the Evolution of Cooperation

### 2020-10-25 ms/main.tex
revised and verified modifier model

\subsection*{Modifiers of social association}

We now analyze the evolution of social association under perfect vertical transmission, $v=1$.
We assume a population at a stable coexistence of the two phenotypes, cooperation $A$ and defection $B$, such that the frequency of $A$ among parents is $\tilde{p}^*$ (
\autoref{eq:vert_hori_equilibrium}).
Note that for stable coexistence to occur, we assume horizontal bias for defection, $T_A < T_B$, and an intermediate cost of cooperation, $\gamma_2 < c < \gamma_1$ (\autoref{eq:cost_boundaries})

The stable population mean fitness is $\bar{w}^* = 1 + \tilde{p}^*(b-c)$ (\autoref{eq:mean_fitness}), which is increasing in $\tilde{p}^*$. 
Therefore, to determine the effect of increasing $\alpha$ on the stable population mean fitness, we must analyze its effect on $\tilde{p}^*$, 
\begin{equation} \label{eq:mean_fitness_stable_coexistence_derivative}
  \frac{\partial \tilde{p}^*}{\partial \alpha} 
%  =\frac{-b^2T_A (1-\alpha) (T_A-T_B) + b(T_A-T_B)(c(1-T_B) - b \alpha T_A - (T_A-T_B))}{b^2 (1-\alpha)^2 (T_A-T_B)^2} 
%  = \frac{b^2T_A(T_B-T_A)-bc(1-T_B)(T_B-T_A) - b(T_B-T_A)^2}{b^2 (1-\alpha)^2 (T_A-T_B)^2} \;.
  = \frac{b T_A - c(1-T_B) + (T_A-T_B)}{b (1-\alpha)^2 (T_B-T_A)} \;.
\end{equation} 
Note that stable coexistence implies $c<\gamma_1$, and because $\alpha<1$, we have
\begin{equation}
c < \gamma_1 = \frac{b \alpha T_A + (T_A-T_B)}{1-T_B} < \frac{b T_A + (T_A-T_B)}{1-T_B}.
\end{equation} 
Therefore, $b T_A - c(1-T_B) - (T_B-T_A)>0$, and since $T_A<T_B$, the derivative $\partial \tilde{p}^* / \partial \alpha$ is positive, and the population mean fitness increases as social association $\alpha$ increases.

We found that if the social association increases, the population mean fitness will increase.
But can an allele that increases the social association evolve? 
To answer this question, we extend our model to include a ``modifier locus''~\citep{Liberman1986,Liberman1988}.
The function of this modifier locus is to determine the social association.
It has no direct effect on fitness.
We assume that the modifier locus has two alleles, $M$ and $m$, which induce association probabilities $\alpha_1$ and $\alpha_2$, respectively, and that initially only $M$ is present.
Suppose that the population evolves to a stable equilibrium when only $M$ is present; we check the local stability of this equilibrium to the introduction of the allele $m$ at the modifier locus. This is called ``external stability''; For more details on external stability, see \citet{Altenberg2017}.

We define the frequencies of the pheno-genotypes $AM$, $BM$, $Am$, and $Bm$ as $\vec{\tilde{p}}= (\tilde{p}_1$, $\tilde{p}_2$, $\tilde{p}_3$, $\tilde{p}_4)$. 
The frequencies of the pheno-genotypes in the next generation are defined by the recursion system 
\begin{equation} \label{eq:next_gen_p_1}
  \begin{aligned}
	% p1
  \bar{w}\tilde{p}_1' & = \tilde{p}_1(\tilde{p}_1+\tilde{p}_3)(1+b-c)(1 - (1-\alpha_1)(\tilde{p}_2 + \tilde{p}_4)T_B) \\
  &+ \tilde{p}_1(\tilde{p}_2 + \tilde{p}_4)(1-c)(1-\alpha_1T_B(\tilde{p}_1 + \tilde{p}_3) - T_B(\tilde{p}_2 + \tilde{p}_4)) \\
  &+ \tilde{p}_2(\tilde{p}_1 + \tilde{p}_3)(1+b)T_A(\tilde{p}_1 + \tilde{p}_3 + \alpha_1(\tilde{p}_2 + \tilde{p}_4)) \\
  &+ \tilde{p}_2(\tilde{p}_2 + \tilde{p}_4)(\tilde{p}_1 + \tilde{p}_3)(1-\alpha_1)T_A 
\\
	% p2
  \bar{w}\tilde{p}_2' & = \tilde{p}_2(\tilde{p}_2+\tilde{p}_4)(1 - (1-\alpha_1)(\tilde{p}_1 + \tilde{p}_3)T_A) \\
  &+ \tilde{p}_2(\tilde{p}_1 + \tilde{p}_3)(1+b)(1-\alpha_1 T_A(\tilde{p}_2 + \tilde{p}_4) - T_A(\tilde{p}_1 + \tilde{p}_3))\\
  &+ \tilde{p}_1(\tilde{p}_2 + \tilde{p}_4)(1-c)(\alpha_1 T_B + (1-\alpha_1)(\tilde{p}_2 + \tilde{p}_4)T_B) \\
  &+ \tilde{p}_1(\tilde{p}_1 + \tilde{p}_3)(1+b-c)(1-\alpha_1)(\tilde{p}_2 + \tilde{p}_4)T_B 
\\
	% p3
  \bar{w}\tilde{p}_3' & = \tilde{p}_3(\tilde{p}_1+\tilde{p}_3)(1+b-c)(1 - (1-\alpha_2)(\tilde{p}_2 + \tilde{p}_4)T_B) \\
  &+ \tilde{p}_3(\tilde{p}_2 + \tilde{p}_4)(1-c)(1-\alpha_2T_B(\tilde{p}_1 + \tilde{p}_3) - T_B(\tilde{p}_2 + \tilde{p}_4)) \\
  &+ \tilde{p}_4(\tilde{p}_1 + \tilde{p}_3)(1+b)T_A(\tilde{p}_1 + \tilde{p}_3 + \alpha_2(\tilde{p}_2 + \tilde{p}_4)) \\
  &+ \tilde{p}_4(\tilde{p}_2 + \tilde{p}_4)(\tilde{p}_1 + \tilde{p}_3)(1-\alpha_2)T_A 
\\
	% p4
  \bar{w}\tilde{p}_4' & = \tilde{p}_4(\tilde{p}_2 + \tilde{p}_4)(1 - (1-\alpha_2)(\tilde{p}_1 + \tilde{p}_3)T_A) \\
  &+ \tilde{p}_4(\tilde{p}_1 + \tilde{p}_3)(1+b)(1-\alpha_2T_A(\tilde{p}_2 + \tilde{p}_4)-T_A(\tilde{p}_1 + \tilde{p}_3))\\
  &+ \tilde{p}_3(\tilde{p}_2 + \tilde{p}_4)(1-c)(\alpha_2T_B + (1-\alpha_2)(\tilde{p}_2 + \tilde{p}_4)T_B) \\
  &+ \tilde{p}_3(\tilde{p}_1 + \tilde{p}_3)(1+b-c)(1-\alpha_2)(\tilde{p}_2 + \tilde{p}_4)T_B \;,
  \end{aligned}
\end{equation}
%which we can write as 
%\begin{equation}
%\bar{w} \vec{\tilde{p}} = F(\vec{\tilde{p}}),
%\end{equation}
where $\bar{w} = 1 + (b-c)\cdot(\tilde{p}_1 + \tilde{p}_3)$ is the population mean fitness.% and $\vec{\tilde{p}} = (\tilde{p}_1,\tilde{p}_2,\tilde{p}_3,\tilde{p}_4)$.

The local stability of $\vec{\tilde{p}^*} = (\tilde{p}^*, 1-\tilde{p}^*, 0, 0)$, the equilibrium when only allele $M$ is present (see \autoref{eq:vert_hori_equilibrium}), to the introduction of allele $m$ is determined by the linear approximation $\vec{L}^*$ of the transformation in \autoref{eq:next_gen_p_1} near $\vec{\tilde{p}^*}$ (i.e., the Jacobian of the transformation at the equilibrium).
$\vec{L}^*$ is known to have a block structure, with the diagonal blocks occupied by the matrices $\vec{L}^*_{in}$ and $\vec{L}^*_{ex}$.
The latter is the external stability matrix: the linear approximation to the transformation near $\vec{\tilde{p}^*}$ involving only the phono-genotypes $Am$ and $Bm$. Because we assume that $\vec{\tilde{p}^*}$ is internally stable (i.e. locally stable to small perturbations in the frequencies of $AM$ and $BM$), the stability of 
$\vec{\tilde{p}^*}$ is determined by the eigenvalues of the external stability matrix $\vec{L}^*_{ex}$, which is derived from \autoref{eq:next_gen_p_1} as
\begin{equation}
\mathbf{L}^*_{ex} = \frac{1}{\bar{w}^*} \begin{bmatrix}
	 \frac{\partial \bar{w} \tilde{p}_3'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) &
	 \frac{\partial \bar{w}  \tilde{p}_3'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) \\
	 \frac{\partial \bar{w}  \tilde{p}_4'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) &
	 \frac{\partial \bar{w}  \tilde{p}_4'}{\partial \tilde{p}_4} (\vec{\tilde{p}}^*)
\end{bmatrix} \;.
\end{equation}
If the eigenvalues of $\mathbf{L}^*_{ex}$ are less than 1, then the equilibrium $\vec{\tilde{p}}$ is externally stable and allele $m$ cannot invade the population of allele $M$.

\begin{equation} \label{eq:partial_derivatives}
  \begin{aligned}
  &D_{33} = \frac{\partial\bar{w}\tilde{p}_3'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) = b(\tilde{p}^*-(1-\alpha_2)T_B(\tilde{p}^*-\tilde{p}^{*2}))+(1-c)(1+\tilde{p}^*T_B-T_B)\\
  &D_{34} = \frac{\partial\bar{w}\tilde{p}_3'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) = bT_A\tilde{p}^*(\tilde{p}^*+\alpha_2(1-\tilde{p}^*))+\tilde{p}^*T_A\\
  &D_{43} =\frac{\partial\bar{w}\tilde{p}_4'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) = (1-\tilde{p}^*)(1-c)T_B+b\tilde{p}^*(1-\alpha_2)(1-\tilde{p}^*)T_B\\
  &D_{44} =\frac{\partial\bar{w}\tilde{p}_4'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) = 1-\tilde{p}^*T_A+ b\tilde{p}^*(1-\alpha_2T_A(1-\tilde{p}^*)-T_A\tilde{p}^*)\\
  \end{aligned}
\end{equation}
Looking on the greater eigenvalue of $\mathbf{L}^*_{ex}$ $\lambda_1$:
\begin{equation} \label{eq:eigenvalues}
  \lambda_1 = \frac{D_{33} + D_{44} + \sqrt{(D_{33}+D_{44})^2-4*(D_{33}+D_{44}-D_{43}D_{34})}}{2} 
\end{equation}
Using SymPy \emph{SymPy} \citep{Meurer2017}, a Python library for symbolic mathematics we get that $\lambda_1 > 1$ when:
\begin{equation} \label{eq:eigenvalues_greater_than_1_condition}
 \alpha_2 > \frac{b\tilde{p}^*(T_B-T_A) + T_B - T_A  + c (1-T_B)}{b*(T_A(1-\tilde{p}^*) + T_B\tilde{p}^*)}
\end{equation}
Using \autoref{eq:vert_hori_equilibrium} we get that $\lambda_1 > 1$ when:
\begin{equation} \label{eq:eigenvalues_greater_than_1_final_condition}
  \alpha_2 > \alpha_1
 \end{equation}
 % TODO: make this result

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Evolution of social association}

We now analyze the evolution of social association under perfect vertical transmission, $v=1$.
We assume a population at a stable coexistence of the two phenotypes, cooperation $A$, and defection $B$, such that the frequency of $A$ among parents is $\tilde{p}^*$ (
\autoref{eq:vert_hori_equilibrium}).
Note that for stable coexistence to occur, we assume horizontal bias for defection, $T_A < T_B$, and an intermediate cost of cooperation, $\gamma_2 < c < \gamma_1$ (\autoref{eq:cost_boundaries})

The stable population mean fitness is $\bar{w}^* = 1 + \tilde{p}^*(b-c)$ (\autoref{eq:mean_fitness}), which is increasing in $\tilde{p}^*$. 
Therefore, to determine the effect of increasing $\alpha$ on the stable population mean fitness, we must analyze its effect on $\tilde{p}^*$, 
\begin{equation} \label{eq:mean_fitness_stable_coexistence_derivative}
  \frac{\partial \tilde{p}^*}{\partial \alpha} 
%  =\frac{-b^2T_A (1-\alpha) (T_A-T_B) + b(T_A-T_B)(c(1-T_B) - b \alpha T_A - (T_A-T_B))}{b^2 (1-\alpha)^2 (T_A-T_B)^2} 
%  = \frac{b^2T_A(T_B-T_A)-bc(1-T_B)(T_B-T_A) - b(T_B-T_A)^2}{b^2 (1-\alpha)^2 (T_A-T_B)^2} \;.
  = \frac{b T_A - c(1-T_B) + (T_A-T_B)}{b (1-\alpha)^2 (T_B-T_A)} \;.
\end{equation} 
Note that stable coexistence implies $c<\gamma_1$, and because $\alpha<1$, we have
\begin{equation}
c < \gamma_1 = \frac{b \alpha T_A + (T_A-T_B)}{1-T_B} < \frac{b T_A + (T_A-T_B)}{1-T_B}.
\end{equation} 
Therefore, the numerator in \autoref{eq:mean_fitness_stable_coexistence_derivative} is positive.
Since $T_A<T_B$, the denominator in \autoref{eq:mean_fitness_stable_coexistence_derivative} is also positive, and hence the derivative $\partial \tilde{p}^* / \partial \alpha$ is positive.
Thus, the population mean fitness increases as social association $\alpha$ increases.

We found that if social association increases, the population mean fitness also increases.
But can an allele that increases social association evolve? 
To answer this question, we extend our model to include a ``modifier locus''~\citep{Liberman1986,Liberman1988} that determines social association, but has no direct effect on fitness.
We assume that the modifier locus has two alleles, $M$ and $m$, which induce social associations $\alpha_1$ and $\alpha_2$, respectively.
Suppose that the population evolves to a stable equilibrium when only allele $M$ is present; we check the local stability of this equilibrium to the introduction of allele $m$ at the modifier locus; This is called ``external stability'', see \citet{Altenberg2017}.

We define the frequencies of the pheno-genotypes $AM$, $BM$, $Am$, and $Bm$ as $\vec{\tilde{p}}= (\tilde{p}_1$, $\tilde{p}_2$, $\tilde{p}_3$, $\tilde{p}_4)$. 
The frequencies of the pheno-genotypes in the next generation are defined by the recursion system 
\begin{equation} \label{eq:next_gen_p_1}
  \begin{aligned}
	% p1
  \bar{w}\tilde{p}_1' & = \tilde{p}_1(\tilde{p}_1+\tilde{p}_3)(1+b-c)(1 - (1-\alpha_1)(\tilde{p}_2 + \tilde{p}_4)T_B) \\
  &+ \tilde{p}_1(\tilde{p}_2 + \tilde{p}_4)(1-c)(1-\alpha_1T_B(\tilde{p}_1 + \tilde{p}_3) - T_B(\tilde{p}_2 + \tilde{p}_4)) \\
  &+ \tilde{p}_2(\tilde{p}_1 + \tilde{p}_3)(1+b)T_A(\tilde{p}_1 + \tilde{p}_3 + \alpha_1(\tilde{p}_2 + \tilde{p}_4)) \\
  &+ \tilde{p}_2(\tilde{p}_2 + \tilde{p}_4)(\tilde{p}_1 + \tilde{p}_3)(1-\alpha_1)T_A \;,
\\
	% p2
  \bar{w}\tilde{p}_2' & = \tilde{p}_2(\tilde{p}_2+\tilde{p}_4)(1 - (1-\alpha_1)(\tilde{p}_1 + \tilde{p}_3)T_A) \\
  &+ \tilde{p}_2(\tilde{p}_1 + \tilde{p}_3)(1+b)(1-\alpha_1 T_A(\tilde{p}_2 + \tilde{p}_4) - T_A(\tilde{p}_1 + \tilde{p}_3))\\
  &+ \tilde{p}_1(\tilde{p}_2 + \tilde{p}_4)(1-c)(\alpha_1 T_B + (1-\alpha_1)(\tilde{p}_2 + \tilde{p}_4)T_B) \\
  &+ \tilde{p}_1(\tilde{p}_1 + \tilde{p}_3)(1+b-c)(1-\alpha_1)(\tilde{p}_2 + \tilde{p}_4)T_B \;, 
\\
	% p3
  \bar{w}\tilde{p}_3' & = \tilde{p}_3(\tilde{p}_1+\tilde{p}_3)(1+b-c)(1 - (1-\alpha_2)(\tilde{p}_2 + \tilde{p}_4)T_B) \\
  &+ \tilde{p}_3(\tilde{p}_2 + \tilde{p}_4)(1-c)(1-\alpha_2T_B(\tilde{p}_1 + \tilde{p}_3) - T_B(\tilde{p}_2 + \tilde{p}_4)) \\
  &+ \tilde{p}_4(\tilde{p}_1 + \tilde{p}_3)(1+b)T_A(\tilde{p}_1 + \tilde{p}_3 + \alpha_2(\tilde{p}_2 + \tilde{p}_4)) \\
  &+ \tilde{p}_4(\tilde{p}_2 + \tilde{p}_4)(\tilde{p}_1 + \tilde{p}_3)(1-\alpha_2)T_A \;, 
\\
	% p4
  \bar{w}\tilde{p}_4' & = \tilde{p}_4(\tilde{p}_2 + \tilde{p}_4)(1 - (1-\alpha_2)(\tilde{p}_1 + \tilde{p}_3)T_A) \\
  &+ \tilde{p}_4(\tilde{p}_1 + \tilde{p}_3)(1+b)(1-\alpha_2T_A(\tilde{p}_2 + \tilde{p}_4)-T_A(\tilde{p}_1 + \tilde{p}_3))\\
  &+ \tilde{p}_3(\tilde{p}_2 + \tilde{p}_4)(1-c)(\alpha_2T_B + (1-\alpha_2)(\tilde{p}_2 + \tilde{p}_4)T_B) \\
  &+ \tilde{p}_3(\tilde{p}_1 + \tilde{p}_3)(1+b-c)(1-\alpha_2)(\tilde{p}_2 + \tilde{p}_4)T_B \;,
  \end{aligned}
\end{equation}
%which we can write as 
%\begin{equation}
%\bar{w} \vec{\tilde{p}} = F(\vec{\tilde{p}}),
%\end{equation}
where $\bar{w} = 1 + (b-c)(\tilde{p}_1 + \tilde{p}_3)$ is the population mean fitness.% and $\vec{\tilde{p}} = (\tilde{p}_1,\tilde{p}_2,\tilde{p}_3,\tilde{p}_4)$.

The equilibrium when only allele $M$ is present is  $\vec{\tilde{p}^*} = (\tilde{p}^*, 1-\tilde{p}^*, 0, 0)$, where
\begin{equation} \label{eq:p_tilde_star_alpha_1}
\tilde{p}^*=
\frac{c(1-T_B) - b \alpha_1 T_A - (T_A - T_B)}{b(1-\alpha_1)(T_A-T_B)},
\end{equation}
which we get by setting $\alpha=\alpha_1$ in \autoref{eq:vert_hori_equilibrium}.
Its local stability to the introduction of allele $m$ is determined by the linear approximation $\vec{L}^*$ of the transformation in \autoref{eq:next_gen_p_1} near $\vec{\tilde{p}^*}$ (i.e., the Jacobian of the transformation at the equilibrium).
$\vec{L}^*$ is known to have a block structure, with the diagonal blocks occupied by the matrices $\vec{L}^*_{in}$ and $\vec{L}^*_{ex}$.
The latter is the external stability matrix: the linear approximation to the transformation near $\vec{\tilde{p}^*}$ involving only the phono-genotypes $Am$ and $Bm$.
Because we assume that $\vec{\tilde{p}^*}$ is internally stable (i.e. locally stable to small perturbations in the frequencies of $AM$ and $BM$), the stability of 
$\vec{\tilde{p}^*}$ is determined by the eigenvalues of the external stability matrix $\vec{L}^*_{ex}$, 
\begin{equation}
\mathbf{L}^*_{ex} = \frac{1}{\bar{w}^*} \begin{pmatrix}
	 X &
	 Y \\
	 Z &
	 Q 
\end{pmatrix} \;.
\end{equation}

The elements of $\mathbf{L}^*_{ex}$ are derived from \autoref{eq:next_gen_p_1},
\begin{equation} \label{eq:partial_derivatives}
  \begin{aligned}
%  X &= \frac{\partial\bar{w}\tilde{p}_3'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) = b \big(\tilde{p}^*-(1 - \alpha_2) T_B (\tilde{p}^* - \tilde{p}^{*2})\big) + (1 - c) (1 + \tilde{p}^* T_B - T_B) \;,\\
  X &= \frac{\partial\bar{w}\tilde{p}_3'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) = b \big(1-(1 - \alpha_2) T_B (1 - \tilde{p}^*)\big) \tilde{p}^* + (1 - c) \big(1 - T_B (1 - \tilde{p}^*)\big) \;,\\
%  Y &= \frac{\partial\bar{w}\tilde{p}_3'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) = b T_A \tilde{p}^* \big(\tilde{p}^* + \alpha_2 (1 - \tilde{p}^*)\big) + \tilde{p}^* T_A \;,\\
  Y &= \frac{\partial\bar{w}\tilde{p}_3'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) = b T_A \big(\tilde{p}^* + \alpha_2 (1 - \tilde{p}^*)\big) \tilde{p}^* + T_A \tilde{p}^* \;,\\
% Z &= \frac{\partial\bar{w}\tilde{p}_4'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) = (1 - \tilde{p}^*) (1 - c) T_B + b \tilde{p}^* (1 - \alpha_2)(1 - \tilde{p}^*) T_B \;,\\
  Z &= \frac{\partial\bar{w}\tilde{p}_4'}{\partial \tilde{p}_3}(\vec{\tilde{p}}^*) = (1 - c) T_B (1 - \tilde{p}^*) + b T_B (1 - \alpha_2) \tilde{p}^*(1 - \tilde{p}^*) \;,\\
%  Q &= \frac{\partial\bar{w}\tilde{p}_4'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) = 1 - \tilde{p}^*T_A+ b\tilde{p}^*\big(1 - \alpha_2 T_A (1 - \tilde{p}^*) - T_A \tilde{p}^* \big) \;.
  Q &= \frac{\partial\bar{w}\tilde{p}_4'}{\partial \tilde{p}_4}(\vec{\tilde{p}}^*) = 1 - T_A \tilde{p}^* + b \big(1 - T_A \tilde{p}^* - \alpha_2 T_A (1 - \tilde{p}^*) \big) \tilde{p}^* \;.
  \end{aligned}
\end{equation}

If both eigenvalues of $\mathbf{L}^*_{ex}$ are less than 1, then the equilibrium $\vec{\tilde{p}^*}$ is externally stable and allele $m$ cannot invade the population of allele $M$. 
These eigenvalues are the root of the characteristic polynomial $\lambda^2 -\lambda (X+Q) + XQ - YZ$; the leading eigenvalue $\lambda_1$ is the largest of them,
\begin{equation} \label{eq:eigenvalues}
  \lambda_1 = \frac{X+Q + \sqrt{(X+Q)^2 - 4(XQ-YZ)}}{2} \;.
\end{equation}
Using \emph{SymPy} \citep{Meurer2017}, a Python library for symbolic mathematics, we find that $\lambda_1 > 1$ if 
\begin{equation} \label{eq:eigenvalues_greater_than_1_condition}
\begin{aligned}
 \alpha_2 > 
 \frac{-b (T_A-T_B) \tilde{p}^* - (T_A - T_B)  + c (1-T_B)}{bT_A - b (T_A-T_B) \tilde{p}^*} = %\\
% \frac{-\frac{c(1-T_B) - b \alpha_1 T_A - (T_A - T_B)}{1-\alpha_1} - (T_A - T_B)  + c (1-T_B)}{bT_A - \frac{c(1-T_B) - b \alpha_1 T_A - (T_A - T_B)}{1-\alpha_1}} = \\
% \frac{\frac{-c(1-T_B) + b \alpha_1 T_A + (T_A - T_B)- (1-\alpha_1)(T_A - T_B)  + (1-\alpha_1)c (1-T_B)}{1-\alpha_1}}{\frac{(1-\alpha_1)bT_A - c(1-T_B) + b \alpha_1 T_A + (T_A - T_B)}{1-\alpha_1}} = \\
%  \frac{-c(1-T_B) + b \alpha_1 T_A + (T_A - T_B)- (1-\alpha_1)(T_A - T_B)  + (1-\alpha_1)c (1-T_B)}{(1-\alpha_1)bT_A - c(1-T_B) + b \alpha_1 T_A + (T_A - T_B)} = \\
%\frac{\alpha_1 b  T_A + \alpha_1 (T_A - T_B)  - \alpha_1 c (1-T_B)}{bT_A - c(1-T_B) + (T_A - T_B)} = 
\alpha_1 \;,
\end{aligned}
\end{equation}
which gives the following result.
\\

\begin{result}[Evolution of social association] 
In a population at a stable coexistence between cooperation and defection, a modifier allele can successfully invade the population if it increases the social association.
Such an invasion will, in turn, increase the population mean fitness.
\end{result}
